\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.qmd
Updated refrence for Figure 13

```{r}
#| fig-cap: "Assessing which of the 8 NLDR layouts on the PBMC3k data  (shown in Figure 1) is the better representation using MSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-h). Layout f is universally poor. Layouts a, b, g, h that show large separations between clusters are universally suboptimal. Layout d with little separation performs well at tiny binwidth (where most points are in their own bin) and poorly as binwidth increases. The choice of best is between layouts c and e, that have small separations between oddly shaped clusters. Layout e is the best choice."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-height: 100%

>>>>

```{r}
#| fig-cap: "Assessing which of the 8 NLDR layouts on the PBMC3k data  (shown in @fig-NLDR-variety) is the better representation using MSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-h). Layout f is universally poor. Layouts a, b, g, h that show large separations between clusters are universally suboptimal. Layout d with little separation performs well at tiny binwidth (where most points are in their own bin) and poorly as binwidth increases. The choice of best is between layouts c and e, that have small separations between oddly shaped clusters. Layout e is the best choice."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-height: 100%

### 2024-09-06 paper.tex
Updated refrence for Figure 13

\caption{\label{fig-pbmc-mse}Assessing which of the 8 NLDR layouts on
the PBMC3k data (shown in Figure 1) is the better representation using
MSE for varying binwidth (\(a_1\)). Colour used for the lines and points
in the left plot and in the scatterplots represents NLDR layout (a-h).
Layout f is universally poor. Layouts a, b, g, h that show large
separations between clusters are universally suboptimal. Layout d with
little separation performs well at tiny binwidth (where most points are
in their own bin) and poorly as binwidth increases. The choice of best
is between layouts c and e, that have small separations between oddly
shaped clusters. Layout e is the best choice.}

>>>>

\caption{\label{fig-pbmc-mse}Assessing which of the 8 NLDR layouts on
the PBMC3k data (shown in Figure~\ref{fig-NLDR-variety}) is the better
representation using MSE for varying binwidth (\(a_1\)). Colour used for
the lines and points in the left plot and in the scatterplots represents
NLDR layout (a-h). Layout f is universally poor. Layouts a, b, g, h that
show large separations between clusters are universally suboptimal.
Layout d with little separation performs well at tiny binwidth (where
most points are in their own bin) and poorly as binwidth increases. The
choice of best is between layouts c and e, that have small separations
between oddly shaped clusters. Layout e is the best choice.}
